### 2012-03-29 contents.tex
Adding threats to validity, changing when figure, searching for 'QA team' to confirm results about who.

However, mining bug repositories has its own risks. Previous research has identified problems of missing data \cite{Arand2009} (e.g., rationale, traceability links between reported bug fixes and source code changes), inaccurate data (e.g., misclassification of bugs) \cite{Antoniol2008}, and biased data \cite{Bird2009}. %,Bird2009,Nguyen2010,Ayari2007}.

@@

\begin{figure}
\centering
\mbox{
\subfigure{\includegraphics[width=0.25\textwidth]{milestones}}%\quad
\subfigure{\includegraphics[width=0.25\textwidth]{cliffs} }}
\caption{Number of verifications over time.} \label{fig:when}
\end{figure}

@@

	Table \ref{tab:qa} presents, for each subproject, the number of developers attributed to a QA team (i.e., developers who perform verifications at least 10 times more often than contribute bug fixes), and the proportion of bug verifications they account for. Mass verifications and developers who have not contributed with fixes and verifications were discarded from the analysis.

@@

	In both NetBeans subprojects it is possible to infer the existence of a QA team, composed by approximately 20\% of the developers, performing at least 80\% of all verifications. In the Eclipse subprojects, there is no evidence of a dedicated QA team. In Eclipse/EMF no developer focus specifically on verification. In Eclipse/Platform, 2.4\% of the developers focus on verification tasks, contributing only to 1.1\% of the verifications.

	Although the reported results are based on an arbitrary threshold (10) for the ratio between verifications and fixes, other values (2 and 5) were also used, leading to similar results. The rightmost column of Table \ref{tab:qa} shows the distribution of the ratio, in log scale, where it can be seen that ratios above 10 are uncommon in all projects.

@@

@@

	Researchers should be aware that information about verification techniques may not be common in bug repositories, and that reported verification does not always correspond to actual verification. Some exploration of the data is important to avoid such pitfalls.

>>>>

However, mining bug repositories has its own risks. Previous research has identified problems of missing data \cite{Aranda2009} (e.g., rationale, traceability links between reported bug fixes and source code changes), inaccurate data (e.g., misclassification of bugs) \cite{Antoniol2008}, and biased data \cite{Bird2009}. %,Bird2009,Nguyen2010,Ayari2007}.

@@

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth]{when}
% \mbox{
% \subfigure{\includegraphics[width=0.25\textwidth]{milestones}}%\quad
% \subfigure{\includegraphics[width=0.25\textwidth]{cliffs} }}
\caption{Accumulated number of verifications over time.} \label{fig:when}
\end{figure}

@@

	Table \ref{tab:qa} presents, for each subproject, the number of developers attributed to a QA team (i.e., developers with verifications per fix ratio greater than the threshold of 10), and the proportion of bug verifications they account for. Other threshold values (2 and 5) were also tried for the ratio, leading to similar results. Mass verifications and developers who have not contributed with fixes and verifications were discarded from the analysis.

@@

	In both NetBeans subprojects it is possible to infer the existence of a QA team, composed by approximately 20\% of the developers, performing at least 80\% of all verifications. In the Eclipse subprojects, there is no evidence of a dedicated QA team. Further evidence was found by looking for the substring ``QA team'' in the comments associated with the status \VERIFIED\ and \REOPENED. Comments referring to a QA team were only found in NetBeans subprojects.

	% In Eclipse/EMF no developer focus specifically on verification. In Eclipse/Platform, 2.4\% of the developers focus on verification tasks, contributing only to 1.1\% of the verifications.

	% Although the reported results are based on an arbitrary threshold (10) for the ratio between verifications and fixes, other values (2 and 5) were also used, leading to similar results. The rightmost column of Table \ref{tab:qa} shows the distribution of the ratio, in log scale, where it can be seen that ratios above 10 are uncommon in all projects.

@@

	The main threat to this study is related to construct validity, i.e., to which point the operational definitions of concepts such as QA team and verification phase reflect the theoretical concepts. To mitigate this problem, we have looked for additional information in the text of comments in the bug reports. Further evidence can be gathered by interviewing developers and mining source code repositories.

@@

	Researchers should be aware that information about verification techniques may not be common in bug repositories, and that reported verification does not always correspond to actual verification (e.g., in the case of mass verifications). Some exploration of the data is important to avoid such pitfalls.
